How Drug Usage During Labor and Delivery Affects Infant Health: A Predictive Analysis of APGAR5 Scores

### 2024-11-26 paper/paper.qmd
appendix model details update

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@@

posterior_vs_prior(bayesian_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

@@

plot(bayesian_model, "trace")

>>>>

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check, with the dark line representing the observed data distribution and the lighter lines indicating the posterior predictive distribution. This shows the notable deviation between `y` and `y_rep`, particularly the oscillations in the observed data. It suggests that the model may not fully capture the underlying structure of the observed data and proposes the need for model refinement, such as including additional predictors or modifying priors [@tellingstories].

@fig-ppcheckandposteriorvsprior-2 compares the prior and posterior distributions of the model parameters. Significant shifts, such as for 'Steroids' and 'Chorioamnionitis' suggest these variables have strong impacts on the outcome, while minimal shifts for 'Antibiotics' indicate limited evidence of their effect. We can also note that the credible intervals underscore uncertainty.

@@

# Create a named vector for the full variable names
variable_names <- c(
  "ster" = "Steroids",
  "sigma" = "Residual Std.",
  "indc" = "Induction of Labor",
  "chor" = "Chorioamnionitis",
  "augmt" = "Augmentation of Labor",
  "antb" = "Antibiotics",
  "anes" = "Anesthesia",
  "(Intercept)" = "(Intercept)"
)

# Update the plot with the full variable names
posterior_vs_prior(bayesian_model) +
  theme_minimal() +
  scale_color_manual(
    values = RColorBrewer::brewer.pal(length(variable_names), "Set1"),  # Use the same color palette
    labels = variable_names  # Apply full names to the legend
  ) +
  theme(legend.position = "bottom") +
  coord_flip() +
  scale_x_discrete(labels = variable_names)  # Apply the full names to y-axis

@@

@fig-stanareyouokay-1, which is a trace plot, shows stable and consistent fluctuations around a central value across iterations for all four chains. This suggests that the Bayesian model's Markov Chain Monte Carlo (MCMC) sampling has converged appropriately, ensuring that the posterior distributions are valid for interpretation.

@fig-stanareyouokay-2, which is a Rhat plot, shows that all Rhat values are very close to 1 and none exceed the threshold of 1.05, indicating that the chains have converged well. This suggests that the Markov Chain Monte Carlo (MCMC) sampling has achieved stability and the posterior distributions can be reliably interpreted.

@@

# Create a named vector for full variable names
variable_names <- c(
  "(Intercept)" = "(Intercept)",
  "indc" = "Induction of Labor",
  "augmt" = "Augmentation of Labor",
  "ster" = "Steroids",
  "antb" = "Antibiotics",
  "chor" = "Chorioamnionitis",
  "anes" = "Anesthesia",
  "sigma" = "Residual Standard Deviation"
)

# Extract and relabel trace plots
bayesplot::mcmc_trace(
  as.array(bayesian_model),  # Convert model to array for trace plotting
  pars = names(variable_names),  # Use variable names
  facet_args = list(labeller = ggplot2::labeller(.rows = variable_names))  # Apply custom labels
) +
  theme_minimal() +
  theme(legend.position = "bottom")
